### 2017-05-29 04-experimental-setup.tex
Move exp. setup into GPU section
Tiny refactor experimental wording
Some wording in DAS section

\section{Experimental setup}
\label{sec-experimental}

Unless indicated otherwise, the experiments described in the next sections
were conducted on the VU~Amsterdam and Leiden DAS5 clusters.  The clusters
consists of 68 and 24 compute nodes respectively. Each node is equipped with
a dual 8-core Intel Xeon E5-2630v3 CPU clocked at 2.40GHz, 64GB of memory and
8TB of storage. The nodes of each site are interconnected by FDR~InfiniBand.
Additionally, the VU cluster is fitted with a number of Nvidia GPUs including
GTX~\mbox{Titan-X}, GTX980, K40c and K20m.

To assess the performance of our implementations, we use publicly available
community networks from the SNAP collection~\cite{snapnets}, including the largest
networks. Table~\ref{table-snap}
outlines the graph properties of the networks used.

>>>>

\subsection{Experimental setup}
\label{sec-experimental}

Unless indicated otherwise, all experiments described in this paper
were conducted on the VU~Amsterdam and Leiden DAS5 clusters.  The clusters
consists of 68 and 24 compute nodes respectively. Each node is equipped with
a dual 8-core Intel Xeon E5-2630v3 CPU clocked at 2.40GHz, 64GB of memory and
8TB of storage. The nodes of each site are interconnected by FDR~InfiniBand.
Additionally, the VU cluster is fitted with a number of NVidia GPUs including
GTX~\mbox{Titan-X}, GTX980, K40c and K20m.

To evaluate our implementations, we use publicly available
community networks from the SNAP collection~\cite{snapnets}.
Table~\ref{table-snap}
outlines the graph properties of the networks used.
